Outstanding Title

### 2017-02-24 writing/EpiDraft.Rmd
Fix bugs in meeting

```{r}
library(eesim)
eesim(n_reps = 3, n = 100, central = 50, sd = 5, exposure_type = "continuous", 
      outcome_trend = "curvilinear", average_outcome = 20, rr = 1.10, model = "spline", df_year = 2)
```

@@

```{r}
power_calc(varying = "n", values = c(5, 50, 500), simargs = list(n_reps = 10,
           rr = 1.02, central = 50, sd = 5, exposure_trend = "no trend",
           exposure_amp = .6, exposure_type = "continuous",
           outcome_trend = "cos1", outcome_amp = .6, average_outcome = 100),
           fitargs = list(model = "spline"))
```

>>>>

```{r}
library(eesim)
eesim(n_reps = 3, n = 100, central = 50, sd = 5, outcome_amp = .6, exposure_type = "continuous", outcome_trend = "cos1", average_outcome = 20, rr = 1.10, model = "spline", df_year = 2)
```

@@

```{r}
power_calc(varying = "n", values = c(365*1:3), simargs = list(n_reps = 10,
           rr = 1.5, central = 50, sd = 5, exposure_trend = "no trend",
           exposure_amp = .6, exposure_type = "continuous",
           outcome_trend = "cos1", outcome_amp = .6, average_outcome = 100),
           fitargs = list(model = "spline"))
```
